The elevational structure of a mountain mutualism: richness, abundance, and β-diversity of bumble bees and their floral hosts

### 2021-09-27 code/ms1_rich_abund.Rmd
finished draft of revision + reviewer responses

>>>>

## 3.5 Does flower cover predict BB abundance?
```{r}
ggplot(rich_abund_siteyear, aes(fl.peakabund, bb.peakabund)) +
  geom_point()

ggplot(rich_abund_siteyear, aes(log(fl.peakabund), log(bb.peakabund))) +
  geom_point()

ggplot(rich_abund_siteyear, aes(log(fl.peakabund), bb.peakabund)) +
  geom_point()

library(lme4)
mod <- glm(bb.peakabund ~ log(fl.peakabund) + elev.mean + year,
           data = rich_abund_siteyear)

plot(mod)
summary(mod)
```

### 2021-09-27 ms_1/ms_revision1.Rmd
finished draft of revision + reviewer responses

Environmental gradients generate and maintain biodiversity on Earth. Mountain slopes are among the most pronounced terrestrial environmental gradients, and the elevational structure of species and their interactions can provide unique insight into the processes that govern community assembly and function in mountain ecosystems.

We recorded bumble- bee-flower interactions over three years along an 1400 m elevational gradient in the German Alps. Using nonlinear modeling, we analyze the elevational patterns at the nested levels of species abundance, species β-diversity, and interaction β-diversity.

While floral richness exhibited mid-elevation peak, bumble bee richness increased with elevation before leveling off at the highest sites, demonstrating the exceptional adaptation of these bees to cold temperatures and short growing seasons. At a species level, though, bumble bees exhibited divergent responses to elevation in terms of abundance, with a clear separation between species preferring low vs. high elevations.

@@

Bumble bees (Hymenoptera: *Bombus* spp.) and their floral hosts provide an excellent system in which to study elevational patterns at both the species- and interaction-level. Bumble bees are believed to have arisen in the mountains of Asia during the cooling climate of the Eocene-Oligocene boundary, and their subsequent spread and diversification along mountain corridors and into lowland habitats was likely driven by alternating range expansion during cooling periods and retreat to higher elevations during warming periods [@Hines2008-er; @Stewart2010-jn; @Martinet2018-rb]. Today, they remain characteristically cold-adapted organisms [@Heinrich1994-cv], with peak abundance and diversity in mountain ranges and northern latitudes [@Williams1998-xi]. In these habitats, they are often the dominant guild of flower-visiting insects and the principal pollinators of entomophilous flora [@Goulson2010-lo]. As in the past, so now are mountain habitats critical theaters of ecological change for bumble bees. Warming climates are expected to cause habitat loss and potentially novel competitive pressures [@Kerr2015-dg; @Soroye2020-zb; though see @Guzman2021-my]. At the same time, socioeconomic drivers are causing the reforestation of pastures on mountain slopes and the intensification of agriculture in lowlands and valleys, both of which entail a loss of floral resources for bumble bees [@Tasser2002-om; @Tappeiner2006-jp; @Tasser2007-qo; @Walcher2017-kw].

In this paper, we present a study based on ~13,000 interactions between bumble bees (Hymenoptera: *Bombus*) and their floral hosts recorded along a 1400 m elevation gradient, complemented by corresponding surveys of floral abundance. Using this dataset, we investigate elevational responses of richness, abundance, and β-diversity (i.e. species turnover), both at the level of species (bumble bees and flowering plants, respectively) and at the level of interactions (bumble- bee-flower pairs). Our results reveal nonlinear and, in some cases, contrasting elevational patterns, underscoring the fact that mountain slopes are complex ecological systems where multiple processes interact to produce biological responses. These patterns shed light on the basic ecology of the mountain mutualism between bumble bees and wildflowers, and they suggest how this mutualism might be reshaped by ongoing processes of climate and land use change.

@@

Our study revealed strong and sometimes contrasting patterns of elevational structure in the richness, abundance, and β-diversity of mountain bumble bees and wildflowers. By extending our analysis to the level of species interactions, we show how the elevational patterns within bumble bee and wildflower communities are propagated to the functional relationships between these two guilds. These patterns suggest underlying processes governing the assembly of the bumble- bee-wildflower networks in mountain habitats, shedding light on how this mutualism has evolved in the past and how it will respond to the nascent forces of climate and land use change.

While floral richness exhibited the expected unimodal response to elevation, bumble bee richness responded positive to elevation for nearly the whole gradient, showing only a slight declining trend at the highest sites. The positive response of bumble bee species richness to elevation sets bumble bees apart from most other taxa [@Rahbek1995-oj; @Guo2013-tu; @Peters2016-hf], underscoring their exceptional adaptation to mountain environments. On higher mountains, the increase of bumble bee richness with elevation eventually gives way to a unimodal response, but peak richness is often found above 3000 m [e.g. @Williams1991-zu; @Streinzer2019-bz], 1000 m above the highest peaks in the Berchtesgadener Alps. Thus, in our study system, the positive response of bumble bee richness to elevation encompasses almost the entire mountain slope, in agreement with the findings of @Minachilis2020-xd along a comparable elevation gradient (300-2700 m) at Mt. Olympus, Greece. The positive response of bumble bee richness stands in sharp contrast to the monotonic decline of overall bee richness with elevation in the Berchtesgadener Alps [@Hoiss2012-sn], highlighting the special importance of bumble bees as pollinators where few other bees persist.

The response of overall bumble bee abundance to elevation was approximately flat, but this aggregate pattern concealed divergent species-level responses. The strongly positive responses of *B. mendax*, *B. monticola*, *B. mucidus*, *B. pyrenaeus* are consistent with the known affinity of these species for high-elevation habitats [@Rasmont2010-ci]. At the other extreme, *B. pascuorum* and *B. psithyrus* exhibited a strongly negative responses to elevation. In the case of *B. pascuorum*, this pattern is likely driven by its exceptionally long nesting cycle, which limits its fitness in the short growing seasons of higher elevations [@Neumayer2009-gx]. Growing season length may also explain the lower abundance of *B. psithyrus* at high elevation, since cuckoo bumble bees emerge later than the queens of their host species and must successfully usurp host nests before they can begin to raise brood [@Goulson2010-lo]. Nevertheless, while the divergent responses of bumble bee species to elevation are informative, it is important to emphasize the general robustness of bumble bees to elevational variation. Nine out of the 16 species in our study system did not respond significantly to elevation, and 8 out of 16 were observed across the full span of the gradient.

@@

The roughly sigmoidal pattern of bumble bee β-diversity rate in response to elevation, revealed by our GDM analysis, probably reflects the reciprocal abundance patterns of high- and low-elevation species described above as well as the occurrence of certain rarer species only at middle-elevation sites. As discussed above, though, bumble bee turnover was low over all, demonstrating the robustness of bumble bees to the environmental variation encompassed by our elevation gradient. Floral β-diversity rate also exhibited a sigmoidal pattern, and its inflection point coincides with the tree line ecotone at ~1500 m. The floristic importance of the tree line has been noted in previous work [e.g. @Pellissier2010-kg; @Descombes2017-id], and our study corroborates these findings specifically for the subset of flora visited by bumble bees. Interestingly, the tree line did not constitute a discrete transition to a new equilibrium fo floral composition, but rather a threshold marking the beginning of a process of β-diversity acceleration that holds for the remainder of the elevation gradient. While the most obvious effect of the tree line may be the relatively discrete transition from forest to scrub/grassland, the tree line also initiates a process of angiosperm species attrition that proceeds at a rate of about 40 species per 100 m [@Korner2003-sc]. Indeed, the accelerated β-diversity we observed above the tree line mirrors simultaneous patterns of decreasing floral richness and abundance **(Figures 3B, 4B)**.

In contrast, the rate of interaction β-diversity exhibited a late and very pronounced acceleration at ~1800 m, indicating that the two highest sites (at 1984 m and 2032 m) differed strongly in interaction composition from those ~200 m below them. At these highest sites, the growing season is very short and vegetation is sparse, giving way to bare rock and scree landscapes, and it may be that the last 200 m interval of our elevation gradient imposes the most stringent environmental filter. It is interesting that interaction β-diversity did not exhibit the inflection point at the tree line ecotone (~1500 m) that we saw for floral β-diversity, despite the fact that overall interaction β-diversity was driven primarily by floral β-diversity. A possible explanation for this pattern is that there could be an elevational lag in bumble bee floral selection such that most bumble bee species do not switch to supra-tree-line floral species when these species first appear, but rather maintain associations with flora whose ranges span the tree line until the extreme species turnover between 1800 and 2000 m forces them to adopt new floral hosts.

The poverty of floral resources at the highest elevations raises the question of why bumble bees choose to forage at such elevations at all. For some species, the selection of high elevation habitats may be influenced by thermal tolerances [@Oyen2016-ng], but that fails to explain the presence of elevation-generalist species (including the majority of the species in our study system) in resource-poor high-elevation habitats. It is possible that nest site limitation at lower elevations drives some bumble bees to establish nests at high elevation, and their ability to forage downslope is subsequently constrained by their flight range, which may be reduced due to the energetic costs of flight in cold temperatures [@Kovac2015-wy]. It is also possible that high elevations, while sparse in absolute floral resources, offer an escape from more competitive conditions at lower elevations where forager density is higher [@Hoiss2015-gv; @Classen2020-nh]. Similarly, higher elevations could also offer an escape from density-dependent parasite and pathogen pressure [@Parsche2018-ar]. Finally, it is worth speculating that an affinity for open, high-elevation habitats might be an evolutionary legacy in mountain bumble bees, since the existence of flower-rich meadows in the forest matrix below the tree line is largely an artifact of human land use arising mainly in the last 500 years of bumble bees' evolutionary history [@Hejcman2013-ca].

Mountains are unique ecological theaters in which the extrinsic forces of climate and land use change interact with intrinsic environmental gradation to shape the ecology of species and their interactions [@Peters2019-km]. Given the elevational patterns of richness, abundance, and β-diversity among bumble bees and wildflowers in our study, what can be said about the response of these communities, and their functional relationships, to climate and land use change? One of the more troubling observations in our study is that the bulk of floral resources were located at low- to mid-elevation. If the process of mid-elevation pasture abandonment continues, the flower-rich meadows that now perforate the forest matrix will eventually close into flower-poor coniferous forest, and bumble bees will be pushed either into the more agriculturally intensified land at lower elevation or the relatively resource-poor open habitat above the tree line. This land- use-driven redistribution of bumble bees will interact with the concomitant process of climate warming, which has already generated measurable upslope shifts in some bumble bees species [@Ploquin2013-da; @Pyke2016-ll; @Marshall2020-pc], sometimes resulting in increased species richness at higher elevations [@Fourcade2019-ct]. Under this scenario, the high-elevation bumble bees in the Berchtesgadener Alps can be expected to face increased densities of low-elevation or elevation-generalist congeners, and the introduction of competing bumble bee species in a given habitat can have strong effects both on the fitness of their congeners and on patterns of floral visitation [@Nagamitsu2010-wi; @Brosi2013-mu; @Ishii2013-sm]. Nevertheless, the tolerance of bumble bees for a relatively broad climate envelope together with their long flight range may enable them to cope with climate and land use change better than their floral mutualists. The flowering plant community in our study system was strongly structured by elevation, and there is evidence that the upslope movement of plants in response to warming temperatures may outpace that of bumble bees [@Marshall2020-pc; though see @Pyke2016-ll]. Moreover, it is the plant community that experiences the direct effects of pasture abandonment at mid-elevation and agricultural intensification at low-elevation.

Finally, our study has focused on contemporary elevational patterns of mountain bumble bees and wildflowers, explored the processes that might regulate them, and related these processes to the nascent pressures of climate and land use change. Mountains are, however, inherently dynamic systems, and have been such throughout the co-evolutionary history of bumble bees and their floral mutualists. Both contemporary patterns and potential responses to global change processes would be elucidated by greater integration with the historical biogeography of bumble bees and wildflowers and their responses to previous episodes of global change [e.g. @Martinet2018-rb].

@@

**Figure 6:** Species-level (A) and interaction-level (B, C) β-diversity plotted against elevational difference. Each point represents the β-diversity (or β-diversity partition) between a pair of sites, and lines represent the overall relationship between β-diversity and elevation difference using binomial regression smooths. Interaction β-diversity (B, C) is partitioned using Poisot et al.’s (2012) notation: WN = unpartitioned β-diversity, ST = β-diversity due to species turnover, OS =  β-diversity due to interaction rewiring, ST.h = β-diversity due to species turnover in the higher trophic level (bumble bees), ST.l = β-diversity due to species turnover in the lower trophic level (plants), and ST.lh =  β-diversity due to joint species turnover in higher and lower trophic levels.

>>>>

Environmental gradients generate and maintain biodiversity on Earth. Mountain slopes are among the most pronounced terrestrial environmental gradients, and the elevational structure of species and their interactions can provide unique insight into the processes that govern community assembly and function in mountain ecosystems. We recorded bumble- bee-flower interactions over three years along an 1400 m elevational gradient in the German Alps. Using nonlinear modeling, we analyzed the elevational patterns at the nested levels of species abundance, species β-diversity, and interaction β-diversity. While floral richness exhibited mid-elevation peak, bumble bee richness increased with elevation before leveling off at the highest sites, demonstrating the exceptional adaptation of these bees to cold temperatures and short growing seasons. At a species level, though, bumble bees exhibited divergent responses to elevation in terms of abundance, with a clear separation between species preferring low vs. high elevations. Overall interaction β-diversity was dominated by strong turnover in the floral community, which exhibited well-defined threshold of β-diversity rate at the tree line ecotone. Turnover of bumble bees along the elevation gradient was modest, with the highest rate of β-diversity occurring over the interval from low- to mid-elevation sites. Interaction β-diversity increased sharply at the upper extreme of the elevation gradient (1800-2000 m), an interval over which we also saw steep decline in floral richness and abundance, suggesting a zone of stringent environmental filtering. Ongoing changes in land use are likely to cause reforestation in resource-rich mid-elevation meadows, forcing bumble bees into agriculturally intensified lowlands or resource-poor highlands, and these effects will interact with climate-induced range shifts in bumble bees and their floral hosts. The contrast between the relative stability of bumble bees community and the dynamism of the floral community in the Berchtesgadener Alps suggests that the strongest effects of climate and land use change on mountain bumble bees will be indirect effects mediated by the responses of their floral hosts.

@@

Bumble bees (Hymenoptera: *Bombus* spp.) and their floral hosts provide an excellent system in which to study elevational patterns at both the species- and interaction-level. Bumble bees are believed to have arisen in the mountains of Asia during the cooling climate of the Eocene-Oligocene boundary, and their subsequent spread and diversification along mountain corridors and into lowland habitats was likely driven by alternating range expansion during cooling periods and retreat to higher elevations during warming periods [@Hines2008-er; @Stewart2010-jn; @Martinet2018-rb]. Today, they remain characteristically cold-adapted organisms [@Heinrich1994-cv], with peak abundance and diversity in mountain ranges and northern latitudes [@Williams1998-xi]. In these habitats, they are often the dominant guild of flower-visiting insects and the principal pollinators of entomophilous flora [@Goulson2010-lo]. As in the past, so now are mountain habitats critical theaters of ecological change for bumble bees. Warming climates are expected to cause habitat loss and potentially novel competitive pressures [@Kerr2015-dg; @Soroye2020-zb; though see @Guzman2021-my]. At the same time, socioeconomic drivers are causing the reforestation of pastures on mountain slopes and the intensification of agriculture in lowlands, both of which entail a loss of floral resources for bumble bees [@Tasser2002-om; @Tappeiner2006-jp; @Tasser2007-qo; @Walcher2017-kw].

In this paper, we present a study based on ~13,000 interactions between bumble bees (Hymenoptera: *Bombus*) and their floral hosts recorded along a 1400 m elevation gradient, complemented by corresponding surveys of floral abundance. Using this dataset, we investigate elevational responses of richness, abundance, and β-diversity, both at the level of species (bumble bees and flowering plants, respectively) and at the level of interactions (bumble- bee-flower pairs). Our results reveal nonlinear and, in some cases, contrasting elevational patterns, underscoring the fact that mountain slopes are complex ecological systems where multiple processes interact to produce biological responses. These patterns shed light on the basic ecology of the mountain mutualism between bumble bees and wildflowers, and they suggest how this mutualism might be reshaped by ongoing processes of climate and land use change.

@@

Our study revealed strong and sometimes contrasting patterns of elevational structure in the richness, abundance, and β-diversity of mountain bumble bees and wildflowers. By extending our analysis to the level of species interactions, we show how the elevational patterns within bumble bee and wildflower communities are propagated to the functional relationships between these two guilds. These patterns suggest underlying processes governing the assembly of bumble- bee-wildflower networks in mountain habitats, shedding light on how this mutualism has evolved in the past and how it may respond to the nascent forces of climate and land use change.

While floral richness exhibited the expected unimodal response to elevation, bumble bee richness responded positively to elevation for nearly the whole gradient, showing only a slight declining trend at the highest sites. The positive response of bumble bee species richness to elevation sets bumble bees apart from most other taxa [@Rahbek1995-oj; @Guo2013-tu; @Peters2016-hf], underscoring their exceptional adaptation to mountain environments. In particular, it stands in sharp contrast to the monotonic decline of overall bee richness with elevation in the Berchtesgadener Alps [@Hoiss2012-sn], highlighting the special importance of bumble bees as pollinators where few other bees persist. On higher mountains, the increase of bumble bee richness with elevation eventually gives way to a unimodal response, but peak richness is often found above 3000 m [e.g. @Williams1991-zu; @Streinzer2019-bz]. In the Berchtesgadener Alps, which reach just over 2000 m, the positive response of bumble bee richness to elevation encompasses almost the entire mountain slope, echoing the findings of @Minachilis2020-xd along a comparable elevation gradient (300-2700 m) at Mt. Olympus, Greece.

The response of overall bumble bee abundance to elevation was approximately flat, but this aggregate pattern concealed divergent species-level responses. The strongly positive responses of *B. mendax*, *B. monticola*, *B. mucidus*, *B. pyrenaeus* are consistent with the known affinity of these species for high-elevation habitats [@Rasmont2010-ci]. At the other extreme, *B. pascuorum* and the *B. psithyrus* species group exhibited strongly negative responses to elevation. In the case of *B. pascuorum*, this pattern is likely driven by its exceptionally long nesting cycle, which limits its fitness in the short growing seasons of higher elevations [@Neumayer2009-gx]. Growing season length may also explain the lower abundance of *B. psithyrus* at high elevation, since cuckoo bumble bees must emerge later than the queens of their host species and then successfully usurp host nests before they can begin to raise brood [@Goulson2010-lo]. Nevertheless, while the divergent responses of bumble bee species to elevation are informative, it is important to emphasize the overall robustness of bumble bees to elevational variation. Nine out of the 16 species in our study system did not respond significantly to elevation, and 8 out of 16 were observed across the full span of the gradient.

@@

The roughly sigmoidal pattern of bumble bee β-diversity rate in response to elevation, revealed by our GDM analysis, probably reflects both the reciprocal abundance patterns of high- and low-elevation species and the occurrence of certain rarer species only at middle-elevation sites. As discussed above, though, bumble bee turnover was low over all, demonstrating the robustness of bumble bees to the environmental variation encompassed by our elevation gradient. Floral β-diversity rate also exhibited a sigmoidal pattern, and its inflection point coincides with the tree line ecotone at ~1500 m. The floristic importance of the tree line has been noted in previous work [e.g. @Pellissier2010-kg; @Descombes2017-id], and our study corroborates these findings specifically for the subset of flora visited by bumble bees. Interestingly, the tree line did not constitute a discrete transition to a new equilibrium of species composition, but rather a threshold marking the beginning of a process of β-diversity acceleration that continued for the remainder of the elevation gradient. While the most obvious effect of the tree line may be the relatively discrete transition from forest to scrub/grassland, the tree line also initiates a process of angiosperm species attrition that proceeds at a rate of about 40 species per 100 m [@Korner2003-sc], and the accelerated β-diversity we observed above the tree line mirrors simultaneous patterns of decreasing floral richness and abundance **(Figures 3B, 4B)**.

In contrast, the rate of interaction β-diversity exhibited a late and very pronounced acceleration at ~1800 m, indicating that the two highest sites at 1984 m and 2032 m differed strongly in interaction composition from the sites ~200 m below them. At these highest sites, the growing season is very short and vegetation is sparse, giving way to bare rock and scree landscapes, and it may be that the last 200 m interval of our elevation gradient imposes the most stringent environmental filter. It is interesting that interaction β-diversity did not exhibit the inflection point at the tree line ecotone (~1500 m) that we saw for floral β-diversity, despite the fact that overall interaction β-diversity was driven primarily by the turnover of the floral community. A possible explanation for this pattern is that there could be an elevational lag in bumble bee floral selection such that most bumble bee species do not switch to supra-tree-line floral species when these species first appear, but rather maintain associations with flora whose ranges span the tree line until the extreme species turnover between 1800 and 2000 m forces them to adopt new floral hosts.     
The poverty of floral resources at the highest elevations raises the question of why bumble bees choose to forage at such elevations at all. For some species, the selection of high elevation habitats may be influenced by thermal tolerances [@Oyen2016-ng], but that fails to explain the presence of elevation-generalist species (including the majority of the species in our study system) in resource-poor high-elevation habitats. It is possible that nest site limitation at lower elevations drives some bumble bees to establish nests at high elevation, and their ability to forage downslope is subsequently constrained by their flight range, which may be reduced due to the energetic costs of flight in cold environments [@Kovac2015-wy]. It is also possible that high elevation landscapes, while sparse in absolute floral resources, offer an escape from more competitive conditions at lower elevations where forager density is higher [@Hoiss2015-gv; @Classen2020-nh]. Similarly, higher elevations could also offer an escape from density-dependent parasite and pathogen pressure [@Parsche2018-ar]. Finally, it is worth speculating that an affinity for open, high-elevation habitats might be an evolutionary legacy in mountain bumble bees, since the existence of flower-rich meadows in the forest matrix below the tree line is largely an artifact of human land use arising mainly in the last 500 years of bumble bees' evolutionary history [@Hejcman2013-ca].

Mountains are unique ecological theaters in which the extrinsic forces of climate and land use change interact with intrinsic environmental gradation to shape the ecology of species and their interactions [@Peters2019-km]. Given the elevational patterns of richness, abundance, and β-diversity among bumble bees and wildflowers in our study, what can be said about the response of these communities, and their functional relationships, to climate and land use change? If the process of mid-elevation pasture abandonment continues, the flower-rich meadows that now perforate the forest matrix will eventually close into flower-poor coniferous forest, and bumble bees will be pushed either into the more agriculturally intensified land at lower elevation or the relatively resource-poor open habitat above the tree line. This land- use-driven redistribution of bumble bees will interact with the concomitant process of climate warming, which has already generated measurable upslope shifts in some bumble bees species [@Ploquin2013-da; @Pyke2016-ll; @Marshall2020-pc], sometimes resulting in increased species richness at higher elevations [@Fourcade2019-ct]. Under this scenario, high-elevation bumble bees can be expected to face increased densities of low-elevation or elevation-generalist species, and the introduction of competing bumble bee species in a given habitat can have strong effects both on the fitness of their congeners and on patterns of floral visitation [@Nagamitsu2010-wi; @Brosi2013-mu; @Ishii2013-sm]. Nevertheless, the tolerance of bumble bees for a relatively broad climate envelope together with their long flight range may enable them to cope with climate and land use change better than their floral mutualists. The flowering plant community in our study system was strongly structured by elevation, and there is evidence that the upslope movement of plants in response to warming temperatures may outpace that of bumble bees [@Marshall2020-pc; though see @Pyke2016-ll]. Moreover, it is the plant community that experiences the direct effects of land use change. Thus, it may be that the strongest effects of climate and land use change on mountain bumble bees will be indirect effects mediated by changes in the floral community.

Finally, our study has focused on contemporary elevational patterns of mountain bumble bees and wildflowers, exploring the processes that might regulate them, and relating these processes to the nascent pressures of climate and land use change. Mountains, however, have been inherently dynamic systems throughout the co-evolutionary history of bumble bees and their floral mutualists [e.g. @Hines2008-er; @Martinet2018-rb]. Both contemporary patterns and potential responses to global change processes would be elucidated by greater integration with the historical biogeography of bumble bees and wildflowers and their responses to previous episodes of global change.

@@

**Figure 6:** Species-level (A) and interaction-level (B, C) β-diversity (in terms of proportional turnover) plotted against elevational difference. Each point represents the β-diversity (or β-diversity partition) between a pair of sites, and lines represent the overall relationship between β-diversity and elevation difference using binomial regression smooths. Interaction β-diversity (B, C) is partitioned using Poisot et al.’s (2012) notation: WN = unpartitioned β-diversity, ST = β-diversity due to species turnover, OS =  β-diversity due to interaction rewiring, ST.h = β-diversity due to species turnover in the higher trophic level (bumble bees), ST.l = β-diversity due to species turnover in the lower trophic level (plants), and ST.lh =  β-diversity due to joint species turnover in higher and lower trophic levels.
